Map of 2018 snow algae sample locations

### 2019-11-04 code/2018_sample_map.Rmd
minor, renamed obj

full_map <- ggmap(algae_map, extent = "device") +
  # jitter points to make it easier to read
  geom_point(data = field, 
              size = 2, alpha=0.5, 
              width = 0.05, height = 0.05, # specify jitter
              aes(color=elev_m)) +
  scale_color_gradientn(colours = terrain.colors(8)[1:7], limits = c(850,2200)) +
  geom_point(data = city_coords, shape = 15) +
  geom_text(data = city_coords, aes(label = name), hjust = 1.1)+
  labs(title = "Snow algae sample sites, summer 2018", color="Elevation (m)")

@@

# ggsave(filename = here("")

>>>>

full_map <- ggmap(algae_map, extent = "device") +
  # jitter points to make it easier to read
  geom_point(data = field, 
              size = 2, alpha=0.5, 
              width = 0.05, height = 0.05, # specify jitter
              aes(color=elev_m)) +
  scale_color_gradientn(colours = terrain.colors(8)[1:7], limits = c(850,2200)) +
  geom_point(data = cities, shape = 15) +
  geom_text(data = cities, aes(label = name), hjust = 1.1)+
  labs(title = "Snow algae sample sites, summer 2018", color="Elevation (m)")

@@

ggsave(filename = here::here("manuscript/figs/map.png"), plot=full_map)
